### 2016-01-15 paper.tex
Remove awkward comma per @wosnik
For --> of

As a cross-flow turbine, the RM2 blades experience large variations in angles of
attack as they rotate about their axis (``cross-flow turbine'' means the axis of
rotation is perpendicular to flow direction---either vertically or
horizontally). These variations become larger as the tip speed ratio
\begin{equation}
    \lambda=\frac{\omega R}{U_\infty},
\end{equation}
where $\omega$ and $R$ are the rotor angular velocity and radius, decreases
\cite{Para2002}. Typically, the maximum angles of attack are sufficiently large
that the blades operate under dynamic stall, which is a complex unsteady process
and deviates significantly from static foil behavior, during part of the
rotation. Furthermore, the higher the solidity of a cross-flow turbine, the
lower the optimal tip-speed ratio at which it operates. Marine Hydrokinetic
(MHK) cross-flow turbines typically have higher solidity than cross-flow wind
turbines (VAWT), and hence operate at lower tip-speed ratios. Since MHK turbines
operate in a higher density fluid, unsteady dynamic effects related to the
blades' pitching motion and flow curvature also become more important when
compared to wind turbines.

The performance of cross-flow MHK turbines thus depends on both Reynolds number
and solidity (note that these issues are related, since an average blade chord
Reynolds number, $Re_{c,\mathrm{avg}} \approx \lambda U_\infty c/ \nu$, can be
expressed in terms of tip speed ratio, the optimal value for which is a function
of solidity). If numerical models are validated with physical model data that
was obtained at insufficiently high Reynolds numbers, it cannot be determined
whether problems with model predictions are caused by Reynolds number effects,
issues related to higher solidity, or both. It is uncertain whether numerical
models validated with physical model data obtained at low Reynolds number should
be considered validated at all, since the scale at which the model will be
applied is orders of magnitude larger. One way to overcome this uncertainty is
to show that the scaled physical model test has become Reynolds number
independent, and therefore validation efforts should be relevant at full-scale.

>>>>

As a cross-flow turbine, the RM2 blades experience large variations in angles of
attack as they rotate about their axis (``cross-flow turbine'' means the axis of
rotation is perpendicular to flow direction---either vertically or
horizontally). These variations become larger at lower tip speed ratio
\begin{equation}
    \lambda=\frac{\omega R}{U_\infty},
\end{equation}
where $\omega$ and $R$ are the rotor angular velocity and radius
\cite{Para2002}. Typically, the maximum angles of attack are sufficiently large
that the blades operate under dynamic stall, which is a complex unsteady process
and deviates significantly from static foil behavior, during part of the
rotation. Furthermore, the higher the solidity of a cross-flow turbine, the
lower the optimal tip-speed ratio at which it operates. Marine Hydrokinetic
(MHK) cross-flow turbines typically have higher solidity than cross-flow wind
turbines (VAWT), and hence operate at lower tip-speed ratios. Since MHK turbines
operate in a higher density fluid, unsteady dynamic effects related to the
blades' pitching motion and flow curvature also become more important when
compared to wind turbines.

The performance of cross-flow MHK turbines thus depends on both Reynolds number
and solidity (note that these issues are related, since an average blade chord
Reynolds number, $Re_{c,\mathrm{avg}} \approx \lambda U_\infty c/ \nu$, can be
expressed in terms of tip speed ratio, the optimal value of which is a function
of solidity). If numerical models are validated with physical model data that
was obtained at insufficiently high Reynolds numbers, it cannot be determined
whether problems with model predictions are caused by Reynolds number effects,
issues related to higher solidity, or both. It is uncertain whether numerical
models validated with physical model data obtained at low Reynolds number should
be considered validated at all, since the scale at which the model will be
applied is orders of magnitude larger. One way to overcome this uncertainty is
to show that the scaled physical model test has become Reynolds number
independent, and therefore validation efforts should be relevant at full-scale.
